Pre-Project Review

### 2021-10-28 article/article.tex
Fix references in article
Update article with example text

\documentclass[sotoncolour]{uosarticle}
\graphicspath{{../figures/}}
\usepackage[round]{natbib}
\hypersetup{colorlinks=true}
%% ----------------------------------------------------------------
%% --------------------THESIS/DOC INFORMATION ---------------------
%\faculty     {Faculty of Science}
%\FACULTY     {\MakeUppercase{\facname}}
\department  {School of Physics and Astronomy}
\DEPARTMENT  {\MakeUppercase{\deptname}}
%\group       {[Group name]}
%\GROUP       {\MakeUppercase{\groupname}}
\title       {BSc Pre-Project Review}
\modulename  {PH4111}
\authors     {180014855}
\date        {\today}

\begin{document}
%% ------------------ FRONT MATTER ORGANISATION -------------------
\frontmatter
\maketitle
\begin{abstract}
This work is about \dots
\end{abstract}
\mainmatter
%% ------------------ MAIN MATTER (CONTENT) --------------------
\section{Introduction} \label{sec:Introduction}
Insert introduction here.

\section{Conclusions} \label{sec:Conclusions}
Draw conclusions here.
\acknowledgements{Thanks to ...}
\backmatter
\appendix
\bibliographystyle{plainnat}
\bibliography{UOS}
%% ----------------------------------------------------------------
\section{Stuff} \label{Section:Stuff}
Insert stuff here.
\end{document}
%% ----------------------------------------------------------------

>>>>

\documentclass[sotoncolour]{uosarticle}
\graphicspath{{../figures/}}
\usepackage[round]{natbib}
\hypersetup{colorlinks=true}

\usepackage{blindtext} % todo: removeme

\department  {School of Physics and Astronomy}
\title       {Pre-Project Review}
\modulename  {PH4111}
\authors     {180014855}
\date        {\today}

\begin{document}
\frontmatter
\maketitle
\begin{abstract}
This work is about \dots
\end{abstract}

\mainmatter

\section{Introduction} \label{sec:Introduction}
\blindtext[2]
		\[{\frac{d}{dx}} \int _{a}^{b} f(x,t)\,dt = f{\big (}x, b{\big )} \cdot {\frac {db}{dx}} - f{\big (}x, a{\big )} \cdot {\frac{da}{dx}} + \int _{a}^{b}{\frac{\partial}{\partial x}} f(x,t)\,dt\]
		assuming \(-\infty < a(x)\) and \(b(x) < \infty\).
\blindtext[1]
\begin{equation}\label{eqn:test}
		\int_{-\infty}^{\infty} f(x)\,dx = \int_{-\infty}^{\infty} f(|\alpha| x - \sum_{i}\frac{\gamma_i}{x - \beta_i})\,dx
\end{equation}
	Equation \ref{eqn:test} holds for arbitrary \(\alpha\), \(\gamma_i\), \(\beta_i\).
\blindtext[1]
\begin{equation}
	\int_{0}^{\infty} x^b e^{-a x} dx = \frac{\Gamma(b+1)}{a^{b+1}}
\end{equation}
\begin{equation}
	\int_{0}^{\infty} \frac{x^t}{e^x - 1} \frac{dx}{x} = \zeta(t) \gamma(t)
\end{equation}
\blindtext[1]

\section{Conclusions} \label{sec:Conclusions}
Draw conclusions here.
\blindtext[4]
\begin{table}
\begin{tabular}{c|c|c|c|c|c|c|c}
    {$m$} & {$\Re\{\underline{\mathfrak{X}}(m)\}$} & {$-\Im\{\underline{\mathfrak{X}}(m)\}$} & {$\mathfrak{X}(m)$} & {$\frac{\mathfrak{X}(m)}{23}$} & {$A_m$} & {$\varphi(m)\ /\ ^{\circ}$} & {$\varphi_m\ /\ ^{\circ}$} \\ \toprule
    1  & 16.128 & +8.872 & 16.128 & 1.402 & 1.373 & -146.6 & -137.6 \\
    2  & 3.442  & -2.509 & 3.442  & 0.299 & 0.343 & 133.2  & 152.4  \\
    3  & 1.826  & -0.363 & 1.826  & 0.159 & 0.119 & 168.5  & -161.1 \\
    4  & 0.993  & -0.429 & 0.993  & 0.086 & 0.08  & 25.6   & 90     \\
    5  & 1.29   & +0.099 & 1.29   & 0.112 & 0.097 & -175.6 & -114.7 \\
    6  & 0.483  & -0.183 & 0.483  & 0.042 & 0.063 & 22.3   & 122.5  \\
    7  & 0.766  & -0.475 & 0.766  & 0.067 & 0.039 & 141.6  & -122   \\
    8  & 0.624  & +0.365 & 0.624  & 0.054 & 0.04  & -35.7  & 90     \\
    9  & 0.641  & -0.466 & 0.641  & 0.056 & 0.045 & 133.3  & -106.3 \\
    10 & 0.45   & +0.421 & 0.45   & 0.039 & 0.034 & -69.4  & 110.9  \\
    11 & 0.598  & -0.597 & 0.598  & 0.052 & 0.025 & 92.3   & -109.3 \\
\end{tabular}
\caption{\label{tbl:test}Insert table caption here.}
\end{table}

\blindtext[3]

\acknowledgements{Thanks to ...}

\backmatter
\appendix
\bibliographystyle{plainnat}
\bibliography{references}
%% ----------------------------------------------------------------
\section{Stuff} \label{Section:Stuff}
Insert stuff here.
\end{document}
%% ----------------------------------------------------------------
